The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2013-08-11 script/de/chapters/ellipticcurves.tex
CT Script: Many minor changes (formal improvements and corrections).
CT Script: Minor changes (We replaced in chap 4 and 7 the domain www.cryptosavvy.com, which lost its previous information about [Lenstra1999] and [Lenstra2002] -- Thanks Helmut).

\newpage
\hypertarget{ellcurve}{}
\chapter{Elliptische Kurven}
\label{Chapter_EllipticCurves}
\index{Elliptische Kurven}
(Filipovics B. / Büger M. / Esslinger B. / Oyono R., April 2000,
 Updates: Dez. 2001, Juni 2002, März 2003, Nov. 2009)

@@

Setzt man den Trend, dass sich die Leistung der verfügbaren Rechner im 
Schnitt alle 18 Monate verdoppelt (Gesetz von Moore\index{Gesetz von Moore}\index{Moore, Gordon E.}%
\footnote{empirische Erkenntnis von Gordon Moore, Mitbegründer von Intel,
1965.} ), in die Zukunft fort, so kann man von einer Entwicklung der
sicheren Schlüssellängen wie in Abbildung~\ref{RSAKeylength} ausgehen
\cite{ec:Lenstra1999} (Quelle: Arjen Lenstra und Eric Verheul:
\url{http://cryptosavvy.com/table.htm}).

@@

%--------------------------------------------------------------------
\newpage
\begin{thebibliography}{99999}
\addcontentsline{toc}{section}{Literaturverzeichnis}
    \bibitem[Cassels1991]{ec:Cassels1991} J. W. S. Cassels,
	\index{Cassels 1991} \\ 
	{\em Lectures on elliptic curves}, \\
	Cambridge University Press, 1991, 143 Seiten.
    \bibitem[Koblitz1984]{ec:Koblitz1984}N. Koblitz, 
	\index{Koblitz 1984} \\
	{\em Introduction to elliptic curves and modular forms}, \\
	Graduate Texts in Mathemathics, Springer-Verlag, 1984.
    \bibitem[Koblitz1998]{ec:Koblitz1998}N. Koblitz, 
	\index{Koblitz 1998} \\
	{\em Algebraic aspects of Cryptography. With an appendix on 
	Hyperelleptic curves by Alfred J. Menezes, Yi Hong Wu and Robert 
	J. Zuccherato}, \\
	Springer-Verlag, 1998, 206 Seiten.
    \bibitem[Lenstra1987]{ec:Lenstra1987} H.W. Lenstra, 
        \index{Lenstra 1987} \\
        {\em Factoring integers with elliptic curves}, \\
	Annals of Mathematics 126, pp. 649-673, 1987.
    \bibitem[Lenstra1999]{ec:Lenstra1999} Arjen K. Lenstra, Eric R. Verheul,
	\index{Lenstra/Verheul 1999} \\
        {\em Selecting Cryptographic Key Sizes (1999)}, \\
	Journal of Cryptology: the journal of the International 
	Association for Cryptologic Research \\
	\url{http://www.cryptosavvy.com/cryptosizes.pdf}
    \bibitem[Menezes1993]{ec:Menezes1993}A. J. Menezes, 
	\index{Menezes 1993} \\ 
	{\em Elliptic curve public key cryptosystems}, \\
	Kluwer Academic Publishers, 1993.
    \bibitem[Silverman1986]{ec:Silverman1986} J. Silverman,
	\index{Silverman 1986} \\
	{\em The Arithmetic of Elliptic Curves},\\
	Springer-Verlag, 1986.
    \bibitem[Silverman1992]{ec:Silverman1992}J. Silverman,
	\index{Silverman 1992} \\
	{\em The arithmetic of elliptc curves}, \\
	Graduate Texts in Mathemathics, Springer-Verlag, 1992.
    \bibitem[SilvermanTate1992]{ec:SilvermanTate1992}J. Silverman, J. Tate,
	\index{Silverman/Tate 1992} \\
	{\em Rational points on elliptic curves}, \\
	Springer-Verlag, 1992.
\end{thebibliography}

@@

  \item Schlüssellängen-Vergleich von Arjen Lenstra und Eric Verheul,\\
        \url{http://cryptosavvy.com/table.htm}

>>>>

\newpage
\hypertarget{ellcurve}{}
\chapter{Elliptische Kurven}
\label{Chapter_EllipticCurves}
\index{Elliptische Kurven}
(Filipovics B. / Büger M. / Esslinger B. / Oyono R., April 2000,
 Updates: Dez. 2001, Juni 2002, März 2003, Nov. 2009, Aug. 2013)

@@

Setzt man den Trend, dass sich die Leistung der verfügbaren Rechner im 
Schnitt alle 18 Monate verdoppelt (Gesetz von Moore\index{Gesetz von
Moore}\index{Moore, Gordon E.}\footnote{%
Empirische Erkenntnis von Gordon Moore, Mitbegründer von Intel, 1965.}%
), in die Zukunft fort, so kann man von einer Entwicklung der
sicheren Schlüssellängen wie in Abbildung~\ref{RSAKeylength} ausgehen,
die anhand der Tabelle 1 (auf Seite 32 in \cite{ec:Lenstra1999}) erstellt
wurde.\footnote{%
Weitere Informationen zum Schlüssellängen-Vergleich von Arjen Lenstra und
Eric Verheul, aber auch zu neuereren Untersuchungen bis 2013 finden sich in\\
\url{http://www.keylength.com/biblio/Handbook_of_Information_Security_-_Keylength.pdf}\\
und interaktiv in\\
\url{http://www.keylength.com/en/1/}.
}

@@

%--------------------------------------------------------------------
\newpage
\begin{thebibliography}{99999}
\addcontentsline{toc}{section}{Literaturverzeichnis}
    \bibitem[Cassels1991]{ec:Cassels1991} J. W. S. Cassels,
	\index{Cassels 1991} \\ 
	{\em Lectures on elliptic curves}, \\
	Cambridge University Press, 1991, 143 Seiten.
    \bibitem[Koblitz1984]{ec:Koblitz1984}N. Koblitz, 
	\index{Koblitz 1984} \\
	{\em Introduction to elliptic curves and modular forms}, \\
	Graduate Texts in Mathemathics, Springer-Verlag, 1984.
    \bibitem[Koblitz1998]{ec:Koblitz1998}N. Koblitz, 
	\index{Koblitz 1998} \\
	{\em Algebraic aspects of Cryptography. With an appendix on 
	Hyperelleptic curves by Alfred J. Menezes, Yi Hong Wu and Robert 
	J. Zuccherato}, \\
	Springer-Verlag, 1998, 206 Seiten.
    \bibitem[Lenstra1987]{ec:Lenstra1987} H.W. Lenstra, 
        \index{Lenstra 1987} \\
        {\em Factoring integers with elliptic curves}, \\
	Annals of Mathematics 126, pp. 649-673, 1987.

\bibitem[Lenstra1999]{nt:Lenstra1999} Arjen K. Lenstra, Eric R. Verheul,
     \index{Lenstra/Verheul 1999} \\
     {\em Selecting Cryptographic Key Sizes (1999 + 2001)}, \\
     Journal of Cryptology 14 (2001), 255-293 \\
     \url{http://www.win.tue.nl/~klenstra/key.pdf},
     \url{http://www.cs.ru.nl/E.Verheul/papers/Joc2001/joc2001.pdf},
     \url{http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.20.69&rep=rep1&type=pdf}.
     % Former Link is dead: \url{http://www.cryptosavvy.com/cryptosizes.pdf}.

    \bibitem[Menezes1993]{ec:Menezes1993}A. J. Menezes, 
	\index{Menezes 1993} \\ 
	{\em Elliptic curve public key cryptosystems}, \\
	Kluwer Academic Publishers, 1993.
    \bibitem[Silverman1986]{ec:Silverman1986} J. Silverman,
	\index{Silverman 1986} \\
	{\em The Arithmetic of Elliptic Curves},\\
	Springer-Verlag, 1986.
    \bibitem[Silverman1992]{ec:Silverman1992}J. Silverman,
	\index{Silverman 1992} \\
	{\em The arithmetic of elliptc curves}, \\
	Graduate Texts in Mathemathics, Springer-Verlag, 1992.
    \bibitem[SilvermanTate1992]{ec:SilvermanTate1992}J. Silverman, J. Tate,
	\index{Silverman/Tate 1992} \\
	{\em Rational points on elliptic curves}, \\
	Springer-Verlag, 1992.
\end{thebibliography}

@@

### 2013-08-11 script/de/chapters/numbertheory.tex
CT Script: Minor changes (We replaced in chap 4 and 7 the domain www.cryptosavvy.com, which lost its previous information about [Lenstra1999] and [Lenstra2002] -- Thanks Helmut).

\hypertarget{Chapter_ElementaryNT}{}
\chapter{Einführung in die elementare Zahlentheorie mit Beispielen}
\label{Chapter_ElementaryNT}
(Bernhard Esslinger, Juli 2001; Updates: Nov. 2001, Juni 2002, Mai 2003,
 Mai 2005, März 2006, Juni 2007, Juli 2009, Jan. 2010, Mai 2013) \\

@@

\bibitem[Lenstra1999]{nt:Lenstra1999} Arjen K. Lenstra, Eric R. Verheul,
     \index{Lenstra/Verheul 1999} \\
     {\em Selecting Cryptographic Key Sizes (1999)}, \\
     Journal of Cryptology: the journal of the International 
     Association for Cryptologic Research, \\
     \url{http://www.cryptosavvy.com/cryptosizes.pdf}.

\bibitem[Lenstra2002]{nt:Lenstra2002} \index{Lenstra 2002}
    Arjen K. Lenstra, Adi Shamir, Jim Tomlinson, Eran Tromer,\\
    {\em Analysis of Bernstein's Factorization Circuit},\\
    \url{http://www.cryptosavvy.com/mesh.pdf}.

>>>>

\hypertarget{Chapter_ElementaryNT}{}
\chapter{Einführung in die elementare Zahlentheorie mit Beispielen}
\label{Chapter_ElementaryNT}
(Bernhard Esslinger, Juli 2001; Updates: Nov. 2001, Juni 2002, Mai 2003,
 Mai 2005, März 2006, Juni 2007, Juli 2009, Jan. 2010, Aug. 2013) \\

@@

\bibitem[Lenstra1999]{nt:Lenstra1999} Arjen K. Lenstra, Eric R. Verheul,
     \index{Lenstra/Verheul 1999} \\
     {\em Selecting Cryptographic Key Sizes (1999 + 2001)}, \\
     Journal of Cryptology 14 (2001), 255-293 \\
     \url{http://www.win.tue.nl/~klenstra/key.pdf},
     \url{http://www.cs.ru.nl/E.Verheul/papers/Joc2001/joc2001.pdf},
     \url{http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.20.69&rep=rep1&type=pdf}.
     % Former Link is dead: \url{http://www.cryptosavvy.com/cryptosizes.pdf}.

\bibitem[Lenstra2002]{nt:Lenstra2002} \index{Lenstra 2002}
    Arjen K. Lenstra, Adi Shamir, Jim Tomlinson, Eran Tromer,\\
    {\em Analysis of Bernstein's Factorization Circuit},\\
    \url{http://tau.ac.il/~tromer/papers/meshc.pdf},
    \url{ttp://www.win.tue.nl/~klenstra/fac_circuits.pdf}.
     % Former Link is dead: \url{http://www.cryptosavvy.com/mesh.pdf}.

### 2013-08-11 script/de/chapters/primes.tex
CT Script: Minor changes (We replaced in chap 4 and 7 the domain www.cryptosavvy.com, which lost its previous information about [Lenstra1999] and [Lenstra2002] -- Thanks Helmut).

\newpage
% \hypertarget{Kapitel_2}{}
\chapter{Primzahlen}
\label{Label_Kapitel_Primes}  %Die Kapitelnr. von \label wird per per \ref geholt.
(Bernhard Esslinger, Mai 1999; Updates: Nov. 2000, Dez. 2001, Juni 2003, Mai 2005, März 2006, Juni 2007, Jan. 2010, Mai 2013)

@@

% --------------------------------------------------------------------------
\vskip +35 pt
\subsection{Offene Fragen zu Primzahlzwillingen}

@@

\noindent Das größte bis heute bekannte Primzahlzwillingspaar mit $100.355$
Dezimalstellen\footnote{\url{http://primes.utm.edu}, Oktober 2009}
ist: \[65.516.468.355\cdot 2^{333.333} \pm 1\]

\noindent Bemerkung: Primzahldrillinge gibt es dagegen nur eines: 3, 5, 7.  Bei allen anderen 
Dreierpacks aufeinanderfolgender ungerader Zahlen ist immer eine durch 3 
teilbar und somit keine Primzahl.

\noindent Offen ist:
\begin{itemize}
\item Gibt es unendlich viele oder eine begrenzte Anzahl von Primzahlzwillingen?

\item Gibt es eine Formel für die Anzahl der Primzahlzwillinge pro Intervall?
\end{itemize}

@@

>>>>

\newpage
% \hypertarget{Kapitel_2}{}
\chapter{Primzahlen}
\label{Label_Kapitel_Primes}  %Die Kapitelnr. von \label wird per per \ref geholt.
(Bernhard Esslinger, Mai 1999; Updates: Nov. 2000, Dez. 2001, Juni 2003, Mai 2005, März 2006, Juni 2007, Jan. 2010, Juli 2013)

@@

% --------------------------------------------------------------------------
\vskip +35 pt
\subsection{Offene Fragen zu Primzahlzwillingen und Primzahl-Cousins}

@@

\noindent Das größte heutzutage bekannte Primzahlzwillingspaar
\[3.756.801.695.685\cdot 2^{666.669} \pm 1\] wurde im
Dezember 2011 gefunden und hat $200.700$ Dezimalstellen.\footnote{%
   \url{http://primes.utm.edu/primes},
   \url{http://www.primegrid.com/download/twin-666669.pdf}}

\noindent Offen ist:
\begin{itemize}
\item Gibt es unendlich viele oder eine begrenzte Anzahl von
      Primzahlzwillingen?\footnote{%
      Bemerkung: Primzahl-{\bf Drillinge} gibt es dagegen nur eines: 3, 5, 7.
      Bei allen anderen Dreierpacks aufeinanderfolgender ungerader Zahlen ist
      immer eine durch 3 teilbar und somit keine Primzahl.
                                  }
\item Gibt es eine Formel für die Anzahl der Primzahlzwillinge pro Intervall?
\end{itemize}

\noindent Im Folgenden werden zwei größere Meilensteine erläutert, die dem
Rätsel näher kommen.

\subsubsection{GPY 2003}

@@

\subsubsection{Zhang 2013}

xxxxxxxxxxxxxx

### 2013-08-11 script/en/chapters/ellipticcurves.tex
CT Script: Many minor changes (formal improvements and corrections).
CT Script: Minor changes (We replaced in chap 4 and 7 the domain www.cryptosavvy.com, which lost its previous information about [Lenstra1999] and [Lenstra2002] -- Thanks Helmut).

\newpage
\hypertarget{ellcurve}{}
\chapter{Elliptic Curves}
\label{Chapter_EllipticCurves}
\index{Elliptic curves}
(Filipovics B. / B\"uger M. / Esslinger B. / Oyono R., April 2000,
Updates: Dec. 2001, June 2002, Mar. 2003, Nov. 2009)

@@

The efficiency of a cryptographic algorithm depends on the key length and
the calculation effort that is necessary to provide a prescribed level of
security. The major advantage of ECC compared to RSA is that it requires
much shorter key lengths. If we assume that the computing power increases
by Moore's law (i.~e.\ it doubles every 18 months)\footnote{empirical
knowledge by Gordon Moore, co-founder of Intel, 1965}, then the evolution of
the key lengths for secure communication will be as figure~\ref{RSAKeylength}
\cite{ec:Lenstra1999} (source: Arjen Lenstra and Eric Verheul:
\url{http://cryptosavvy.com/table.htm}).

@@

Nevertheless, thin clients like smart cards usually have to store the (long)
secret key and have to process a digital signature rather than verify one.
Therefore, there is a clear advantage in using ECC in terms of efficiency.
\par
\smallskip
Nowadays, the major problem with ECC implementations is the lack of standardization.
There is only one way to implement RSA, but there are many ways for ECC: One can work with
different sets of numbers, different (elliptic) curves --- described by parameters\footnote{%
see chapter \ref{ECC-Crypto}
} --- ,
and a variety of representations of the elements on the curve. Each choice has its
advantages and disadvantages, and one can certainly construct the most efficient for
each application. However, this causes problems in interoperability. But if all
ECC-tools should be able to communicate with each other, they will have to support
all different algorithms, which might put the advantage of efficient computation and
the need of less storage capacity to the contrary.

@@

    \bibitem[Cassels1991]{ec:Cassels1991} J. W. S. Cassels,
	\index{Cassels 1991} \\
        {\em Lectures on elliptic curves},\\
	Cambridge University Press, 1991, 143 pages.
    \bibitem[Koblitz1984]{ec:Koblitz1984}N. Koblitz, 
	\index{Koblitz 1984} \\
        {\em Introduction to elliptic curves and modular forms},\\
	Graduate Texts in Mathematics, Springer-Verlag, 1984.
    \bibitem[Koblitz1998]{ec:Koblitz1998}N. Koblitz,  
	\index{Koblitz 1998}\\
	{\em Algebraic aspects of Cryptography. With an appendix on 
	Hyperelleptic curves by Alfred J. Menezes, Yi Hong Wu and Robert 
	J. Zuccherato}, \\
	Springer-Verlag, 1998, 206 pages.
    \bibitem[Lenstra1987]{ec:Lenstra1987} H.W. Lenstra, 
        \index{Lenstra 1987} \\
        {\em Factoring integers with elliptic curves}, \\
	Annals of Mathematics 126, pp. 649-673, 1987.
    \bibitem[Lenstra1999]{ec:Lenstra1999} Arjen K. Lenstra, Eric R. Verheul
        \index{Lenstra/Verheul 1999} \\
        {\em Selecting Cryptographic Key Sizes (1999)},\\
	Journal of Cryptology: the journal of the International 
	Association for Cryptologic Research \\
	\url{http://www.cryptosavvy.com/cryptosizes.pdf}
    \bibitem[Menezes1993]{ec:Menezes1993}A. J. Menezes, 
	\index{Menezes 1993} \\
        {\em Elliptic curve public key cryptosystems},\\
	Kluwer Academic Publishers, 1993.
    \bibitem[Silverman1986]{ec:Silverman1986} J. Silverman, 
        \index{Silverman 1986}\\
        {\em The Arithmetic of Elliptic Curves},\\
	Springer-Verlag, 1986.
    \bibitem[Silverman1992]{ec:Silverman1992}J. Silverman,
	\index{Silverman 1992} \\
        {\em The arithmetic of elliptc curves},\\
	Graduate Texts in Mathematics, Springer-Verlag, 1992.
    \bibitem[SilvermanTate1992]{ec:SilvermanTate1992}J. Silverman, J. Tate,
	\index{Silverman/Tate 1992} \\
        {\em Rational points on elliptic curves},\\
	Springer-Verlag, 1992.

@@

   \item Key length comparison by Arjen Lenstra and Eric Verheul,\\
        \url{http://cryptosavvy.com/table.htm}

>>>>

\newpage
\hypertarget{ellcurve}{}
\chapter{Elliptic Curves}
\label{Chapter_EllipticCurves}
\index{Elliptic curves}
(Filipovics B. / B\"uger M. / Esslinger B. / Oyono R., April 2000,
Updates: Dec. 2001, June 2002, Mar. 2003, Nov. 2009, Aug. 2013)

@@

The efficiency of a cryptographic algorithm depends on the key length and
the calculation effort that is necessary to provide a prescribed level of
security. The major advantage of ECC compared to RSA is that it requires
much shorter key lengths.

If we assume that the computing power increases by Moore's law (i.~e.\ it
doubles every 18 months)\footnote{%
Empirical knowledge by Gordon Moore, co-founder of Intel, 1965}%
, then the evolution of the key lengths for secure communication will be as
in figure~\ref{RSAKeylength}, which was generated from table 1 (on page 32 in
\cite{ec:Lenstra1999}).\footnote{%
Further information about key length comparison by Arjen Lenstra und Eric
Verheul, plus more modern evaluations till 2013 can be found in\\
\url{http://www.keylength.com/biblio/Handbook_of_Information_Security_-_Keylength.pdf}\\
and interactively in\\
\url{http://www.keylength.com/en/1/}.
}

@@

Nevertheless, thin clients like smart cards usually have to store the (long)
secret key and have to process a digital signature rather than verify one.
Therefore, there is a clear advantage in using ECC in terms of efficiency.
\par
\smallskip
Nowadays, the major problem with ECC implementations is the lack of
standardization. There is only one way to implement RSA, but there are many
ways for ECC: One can work with different sets of numbers, different (elliptic)
curves --- described by parameters\footnote{%
See chapter \ref{ECC-Crypto}
} --- , and a variety of representations of the elements on the curve. Each
choice has its advantages and disadvantages, and one can certainly construct
the most efficient for each application. However, this causes problems in
interoperability. But if all ECC-tools should be able to communicate with each
other, they will have to support all different algorithms, which might put the
advantage of efficient computation and the need of less storage capacity to the
contrary.

@@

    \bibitem[Cassels1991]{ec:Cassels1991} J. W. S. Cassels,
	\index{Cassels 1991} \\
        {\em Lectures on elliptic curves},\\
	Cambridge University Press, 1991, 143 pages.
    \bibitem[Koblitz1984]{ec:Koblitz1984}N. Koblitz, 
	\index{Koblitz 1984} \\
        {\em Introduction to elliptic curves and modular forms},\\
	Graduate Texts in Mathematics, Springer-Verlag, 1984.
    \bibitem[Koblitz1998]{ec:Koblitz1998}N. Koblitz,  
	\index{Koblitz 1998}\\
	{\em Algebraic aspects of Cryptography. With an appendix on 
	Hyperelleptic curves by Alfred J. Menezes, Yi Hong Wu and Robert 
	J. Zuccherato}, \\
	Springer-Verlag, 1998, 206 pages.
    \bibitem[Lenstra1987]{ec:Lenstra1987} H.W. Lenstra, 
        \index{Lenstra 1987} \\
        {\em Factoring integers with elliptic curves}, \\
	Annals of Mathematics 126, pp. 649-673, 1987.

\bibitem[Lenstra1999]{nt:Lenstra1999} Arjen K. Lenstra, Eric R. Verheul,
     \index{Lenstra/Verheul 1999} \\
     {\em Selecting Cryptographic Key Sizes (1999 + 2001)}, \\
     Journal of Cryptology 14 (2001), 255-293 \\
     \url{http://www.win.tue.nl/~klenstra/key.pdf},
     \url{http://www.cs.ru.nl/E.Verheul/papers/Joc2001/joc2001.pdf},
     \url{http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.20.69&rep=rep1&type=pdf}.
     % Former Link is dead: \url{http://www.cryptosavvy.com/cryptosizes.pdf}.

    \bibitem[Menezes1993]{ec:Menezes1993}A. J. Menezes, 
	\index{Menezes 1993} \\
        {\em Elliptic curve public key cryptosystems},\\
	Kluwer Academic Publishers, 1993.
    \bibitem[Silverman1986]{ec:Silverman1986} J. Silverman, 
        \index{Silverman 1986}\\
        {\em The Arithmetic of Elliptic Curves},\\
	Springer-Verlag, 1986.
    \bibitem[Silverman1992]{ec:Silverman1992}J. Silverman,
	\index{Silverman 1992} \\
        {\em The arithmetic of elliptc curves},\\
	Graduate Texts in Mathematics, Springer-Verlag, 1992.
    \bibitem[SilvermanTate1992]{ec:SilvermanTate1992}J. Silverman, J. Tate,
	\index{Silverman/Tate 1992} \\
        {\em Rational points on elliptic curves},\\
	Springer-Verlag, 1992.

@@

### 2013-08-11 script/en/chapters/numbertheory.tex
CT Script: Minor changes (We replaced in chap 4 and 7 the domain www.cryptosavvy.com, which lost its previous information about [Lenstra1999] and [Lenstra2002] -- Thanks Helmut).

\newpage
\hypertarget{Chapter_ElementaryNT}{}
\chapter{Introduction to Elementary Number Theory with Examples}
\label{Chapter_ElementaryNT}
(Bernhard Esslinger, July 2001; Updates: Dec. 2001, June 2002, May 2003,
 May 2005, March 2006, June 2007, July 2009, Jan. 2010, May 2013) \\

@@

\bibitem[Lenstra1999]{nt:Lenstra1999} Arjen K. Lenstra, Eric R. Verheul
     \index{Lenstra/Verheul 1999} \\
     {\em Selecting Cryptographic Key Sizes (1999)},\\
     Journal of Cryptology: the journal of the International 
     Association for Cryptologic Research, \\
     \url{http://www.cryptosavvy.com/cryptosizes.pdf}.

\bibitem[Lenstra2002]{nt:Lenstra2002} \index{Lenstra 2002}
    Arjen K. Lenstra, Adi Shamir, Jim Tomlinson, Eran Tromer,\\
    {\em Analysis of Bernstein's Factorization Circuit},\\
    \url{http://www.cryptosavvy.com/mesh.pdf}.

>>>>

\newpage
\hypertarget{Chapter_ElementaryNT}{}
\chapter{Introduction to Elementary Number Theory with Examples}
\label{Chapter_ElementaryNT}
(Bernhard Esslinger, July 2001; Updates: Dec. 2001, June 2002, May 2003,
 May 2005, March 2006, June 2007, July 2009, Jan. 2010, Aug. 2013) \\

@@

\bibitem[Lenstra1999]{nt:Lenstra1999} Arjen K. Lenstra, Eric R. Verheul,
     \index{Lenstra/Verheul 1999} \\
     {\em Selecting Cryptographic Key Sizes (1999 + 2001)}, \\
     Journal of Cryptology 14 (2001), 255-293 \\
     \url{http://www.win.tue.nl/~klenstra/key.pdf},
     \url{http://www.cs.ru.nl/E.Verheul/papers/Joc2001/joc2001.pdf},
     \url{http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.20.69&rep=rep1&type=pdf}.
     % Former Link is dead: \url{http://www.cryptosavvy.com/cryptosizes.pdf}.

\bibitem[Lenstra2002]{nt:Lenstra2002} \index{Lenstra 2002}
    Arjen K. Lenstra, Adi Shamir, Jim Tomlinson, Eran Tromer,\\
    {\em Analysis of Bernstein's Factorization Circuit},\\
    \url{http://tau.ac.il/~tromer/papers/meshc.pdf},
    \url{ttp://www.win.tue.nl/~klenstra/fac_circuits.pdf}.
     % Former Link is dead: \url{http://www.cryptosavvy.com/mesh.pdf}.

### 2013-08-11 script/en/chapters/primes.tex
CT Script: German translation of 4.11.5.4 (Shared Primes) from the weekend
CT Script: Minor changes (We replaced in chap 4 and 7 the domain www.cryptosavvy.com, which lost its previous information about [Lenstra1999] and [Lenstra2002] -- Thanks Helmut).

\newpage
% \hypertarget{Kapitel_2}{}
\chapter{Prime Numbers}
\label{Label_Kapitel_Primes}
(Bernhard Esslinger, May 1999; Updates Nov. 2000, Dec. 2001, June 2003, May 2005, March 2006, June 2007, Jan. 2010, May 2013)

@@

Now more than 130,000 volunteers, amateurs and experts, participate in the 
GIMPS project. They connect their computers into the so called ``primenet'', 
organized by the company entropia.

@@

% --------------------------------------------------------------------------
\vskip +35 pt
\subsection{Open questions about twin primes}

@@

\noindent The biggest known twin pair nowadays is \[65,516,468,355\cdot 2^{333,333} \pm 1\]
with $100,355$ decimal digits.\footnote{\url{http://primes.utm.edu}, October 2009}

\noindent Remark: Triplet primes, however, only occur once: 3, 5, 7.  
For all other sets of three consecutive uneven numbers, one of them is 
always divisible by 3 and thus not a prime.

\noindent Open questions are:
\begin{itemize}
\item The number of twin primes: infinitely many or a limited number?

\item Does a formula exist for calculating the number of twin primes per interval?
\end{itemize}

>>>>

\newpage
% \hypertarget{Kapitel_2}{}
\chapter{Prime Numbers}
\label{Label_Kapitel_Primes}
(Bernhard Esslinger, May 1999; Updates Nov. 2000, Dec. 2001, June 2003, May 2005, March 2006, June 2007, Jan. 2010, July 2013)

@@

Now more than 130,000 volunteers, amateurs and experts, participate in the 
GIMPS project. They connect their computers into the so called ``PrimeNet'', 
originally organized by the company Entropia from Scott Kurowski.

@@

% --------------------------------------------------------------------------
\vskip +35 pt
\subsection{Open questions about twin primes and prime cousins}

@@

\noindent The biggest known twin pair is \[3,756,801,695,685\cdot
2^{666,669} \pm 1\] with $200,700$ decimal digits (found in December
2011).\footnote{%
   \url{http://primes.utm.edu/primes},
   \url{http://www.primegrid.com/download/twin-666669.pdf} }

\noindent Open questions are:
\begin{itemize}
\item What is the number of twin primes: Are there infinitely many or only a
      limited number?\footnote{%
      Remark: {\bf Triplet} primes, however, only occur once: 3, 5, 7.  
      For all other sets of three consecutive uneven numbers, one of them is 
      always divisible by 3 and thus not a prime.
                              }
\item Does a formula exist for calculating the number of twin primes per interval?
\end{itemize}

\noindent In the following two major milestones are explained which may allow
to come closer to the riddle.

\subsubsection{GPY 2003}
